\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{tabularx}

% --- Configuration ---
\geometry{top=0.75in, bottom=0.75in, left=0.75in, right=0.75in}
\pagestyle{empty}

% Colors
\definecolor{primary}{RGB}{44, 62, 80}
\definecolor{accent}{RGB}{52, 152, 219}
\definecolor{textgray}{RGB}{80, 80, 80}

% Formatting
\titleformat{\section}{\large\bfseries\color{primary}\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{8pt}
\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=*}
\setlength{\parindent}{0pt}

% Hyperlink Setup
\hypersetup{
    colorlinks=true,
    linkcolor=primary,
    urlcolor=accent,
}

\begin{document}

% --- Header ---
\begin{center}
    {\Huge \textbf{\textcolor{primary}{André Montoia}}} \\ \vspace{4pt}
    {\large \textcolor{accent}{\textbf{Data \& AI Project Manager | Agile Delivery Lead}}} \\ \vspace{6pt}
    \small Lisbon, Portugal | +351 910 031 835 | \href{mailto:andre.montoia@gmail.com}{andre.montoia@gmail.com} | \href{https://linkedin.com/in/andré-montoia-rebêlo}{linkedin.com/in/andré-montoia-rebêlo}
\end{center}

% --- Profile ---
\section{Profile}
Data \& AI Project Manager with over 5 years of experience orchestrating enterprise-grade analytics ecosystems and leading agile transformations. Currently driving the strategic roadmap for Data Analytics Front Ends at Siemens, managing the full lifecycle of platforms including \textbf{Airflow, Qlik Cloud, Anaplan, and SAP Analytics Cloud}. Expertise includes leading cross-functional teams (India, Portugal, Germany) to deliver scalable data solutions and integrating \textbf{Artificial Intelligence and Model Context Protocols (MCP)} into core business analytics.

% --- Skills ---
\section{Core Skills}
\begin{itemize}
    \item \textbf{Data \& AI Platforms:} Qlik Cloud, SAP Analytics Cloud, Anaplan, Airflow, Microsoft Fabric, AI Integrations (MCP)
    \item \textbf{Management:} Agile Methodologies (Scrum Master Certified), Project Management, Stakeholder Alignment, Budgeting
    \item \textbf{Core:} Analytical Thinking, SaaS Migration, Cross-cultural Leadership, Data-Driven Decision Making
\end{itemize}

% --- Experience ---
\section{Professional Experience}

\textbf{Data \& AI Project Lead | Visualizations and UX} \hfill \textit{2022 -- Present} \\
\textit{Siemens AG} \hfill \textcolor{accent}{Lisbon, Portugal}
\begin{itemize}
    \item Leading strategic roadmap and agile delivery for enterprise Data \& AI platforms (Airflow, Qlik Cloud, Anaplan, SAP Analytics Cloud).
    \item Spearheading \textbf{AI \& MCP integrations}, managing global cross-functional squads, and executing SaaS migrations.
    \item Owning budget, procurement, and ROI-driven investment decisions for global analytics tools.
    \item Bridging the gap between technical teams and business leadership, translating complex data requirements into actionable project roadmaps.
\end{itemize}
\vspace{2mm}

\textbf{Data Solution Expert | AI \& Analytics} \hfill \textit{2016 -- 2022} \\
\textit{Siemens AG} \hfill \textcolor{accent}{Alfragide, Portugal}
\begin{itemize}
    \item Delivered enterprise BI solutions as technical lead for Qlik-based platforms.
    \item Engineered performance improvements for on-prem analytics, reducing load times and enhancing user experience.
    \item Maintained high-availability environments ensuring data integrity and system reliability.
    \item Collaborated with stakeholders to translate business needs into technical specifications.
\end{itemize}
\vspace{2mm}

\textbf{IT Systems Administrator} \hfill \textit{2013 -- 2016} \\
\textit{Construção Publica E.P.E} \hfill \textcolor{accent}{Lisbon, Portugal}
\begin{itemize}
    \item Maintained IT infrastructure and system security, resolving incidents and performing upgrades.
\end{itemize}
\vspace{2mm}

\textbf{IT Helpdesk Technician} \hfill \textit{2012 -- 2013} \\
\textit{EDNI Lda} \hfill \textcolor{accent}{Lisbon, Portugal}
\begin{itemize}
    \item Delivered first-line support, logging and tracking technical incidents.
\end{itemize}
\vspace{2mm}

\textbf{Hardware Technician} \hfill \textit{2011 -- 2012} \\
\textit{DECSIS} \hfill \textcolor{accent}{Alfragide, Portugal}
\begin{itemize}
    \item Diagnosed and replaced faulty components, ensuring operational efficiency.
\end{itemize}

% --- Education ---
\section{Education}
\textbf{Postgraduate in Digital Technologies for Management} \hfill \textit{2022 -- 2023} \\
\textit{ISEG – Lisbon School of Economics \& Management}
\begin{itemize}
    \item Specialized in Business Analytics, Cloud Applications, Digital Transformation, Security \& AI.
\end{itemize}

% --- Certifications ---
\section{Certifications}
\begin{itemize}
    \item \textbf{Certified ScrumMaster® (CSM)} -- Scrum Alliance (2025)
    \item \textbf{Advanced Microsoft Power BI} -- LinkedIn Learning (2022)
\end{itemize}

% --- Languages ---
\section{Languages}
\begin{itemize}
    \item \textbf{English:} Fluent (Professional Proficiency)
    \item \textbf{Portuguese:} Native
\end{itemize}

\end{document}
